---
title: "Base R Graphics"
output:
  html_document: 
    theme: spacelab
---

<style type="text/css">
body, td {
   font-size: 10px;
}
code.r{
  font-size: 10px;
}
pre {
  font-size: 14px
}
</style>


# A Simple example

First create the vectrors to use for the plot.

```{r create data frame,cache=TRUE}
dose <- seq(20,60,10)
drugA <- c(16,20,27,40,60)
drugB <- c(15,18,25,31,40)
```

Two lines build the plot. The `abline` function overplots a straight line based on intercept and slope.

```{r simple plot, echo=TRUE, cache=TRUE}
opar <- par(no.readonly=TRUE)
plot(dose, drugA, type="b", lty=2, pch=17)
lines(dose, drugB, type ="b", lty=3, pch=21)
par(opar)
```


### Adding some colour

Here the simple plot again 

```{r color to simple plot, cache=FALSE}
# from https://r-charts.com/base-r/background-color/#background-color-plot
opar <- par(no.readonly=TRUE)
par(bg="#717171", fg="blue")

plot(dose, drugA, ann = FALSE)
lines(dose, drugB)
rect(par("usr")[1], par("usr")[3],
     par("usr")[2], par("usr")[4],
     col = "#A1A1A1") # Color

par(new = plot)

plot(dose, drugA, type="b",
     lty=2, pch=17,
     col = 'blue',
     col.axis = "blue",
     col.lab = "blue",
     col.main = "blue",
     main = "Reponses to drugs A and B",
     xlab = "Dose in Units/kg body weight",
     ylab ="Treatment response"
     )
lines(dose, drugB, type ="b", lty=3, pch=21)
par(opar)
```

# Testing the RColorBrewer package

This package is amazing. My advice is to go check out the palettes available.
There is one for every need and taste.


```{r more color}
library(RColorBrewer)
n <-9
mycolors <- brewer.pal(n, "GnBu")
barplot(rep(1,n), col=mycolors)
```

The web tool for guidance in choosing choropleth map color schemes, based on the research of Dr. Cynthia Brewer can be seen in <https://colorbrewer2.org/#>. It mentions color schemes according to data  type: sequential, diverging, or qualitative.


Here is a quick way to see general preconfigured palettes, from <https://www.r-graph-gallery.com/38-rcolorbrewers-palettes> or <http://applied-r.com/rcolorbrewer-palettes/>.

The three groups of palettes apply to each type fo data as mentioned above.


```{r generate all RColorBrewer palettes}
library(RColorBrewer)
opar <- par(no.readonly = TRUE)
par(mar=c(0,4,0,8)) # bottom, left, top, right
display.brewer.all()
par(opar)
```
